---
title: "___blabla___"
author: "jb"
date: "`r Sys.Date()`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    theme: lumen
    vertical_layout : fill
---
<style>

.navbar {
  background-color:#007A5F;
  border-color:#007A5F;
}
.navbar-brand {
color:white!important;
}
.navbar-nav li a:hover, .navbar-nav > .active > a {
color: #fff !important;

background-color:#44A08B !important;
border-color:#44A08B;
background-image: none !important;
}
.sbframelist ul li.active {
    background-color: #B1A800;
}
.chart-title {
    color: #007A5F;
}

.dataTables_scrollBody {
    max-height: 100% !important;
}

<tag-name style="white-space:pre">text in element&#9;more text</tag-name>
</style>

```{r}
library(raster)
library(tidyverse)
library(leafem)
library(leaflet)
library(downloader)
library(here)
library(USAboundaries)
library(sf)
library(crosstalk)
##running leaflet 2.1.0 to use addRasterRGB from leaflet##

##Data## use once
# ras_path<-"https://www.naturalearthdata.com/http//www.naturalearthdata.com/download/50m/raster/NE1_50M_SR_W.zip"
# downloader::download(ras_path,dest="dataset.zip",mode="wb")
# unzip ("dataset.zip")

#read in file
ras_path1<-here::here('Rcode','rmd',"NE1_50M_SR_W","NE1_50M_SR_W.tif")
ras<-raster::brick(ras_path1)

#vector data
west<- USAboundaries::us_states(resolution = "low") %>% 
  filter(state_name %in% c("California","Utah","Nevada","Arizona")) %>% 
  st_transform(crs=4326)

## crop and mask
ras<-raster::aggregate(ras,fact=20)
```


Main Map
==========

```{r}

useDF<-west

```


```{r}
#create shared data object as SF and as data.frame

sd<-SharedData$new(useDF)

```


Inputs {.sidebar}
--------------------------------
### Filters

```{r map}

 filter_checkbox(
   id = "name",
   label = "name",
   sharedData = sd,
   group = ~name
 )

```



Column {data-width=700}
-------------------------------------

### 

```{r}

leaflet(sd) %>%
     addProviderTiles('Esri.WorldImagery', group = "geo") %>%
   leafem::addRasterRGB(ras, r=1,g=2,b=3) %>% 
     #add states
    addPolygons()
 
rm(sd,useDF) 
```

